Variance reduction for MCMC methods via martingale representations

### 2020-03-11 aap/Revision/vr-mcmc-revision-new.tex
update

\begin{aug}
\author{\snm{D. Belomestny}\thanksref{a,b}\ead[label=e1]{denis.belomestny@uni-due.de}}
\and
\author{\snm{E. Moulines}\thanksref{c, b}\ead[label=e2]{eric.moulines@polytechnique.edu}}
\and
\author{\snm{S. Samsonov}\thanksref{b}\ead[label=e3]{svsamsonov@hse.ru}}
\and
\author{\snm{N. Shagadatov}\thanksref{b}\ead[label=e4]{nshagadatov@edu.hse.ru}}

@@

\PVar_x[\pi_{K,n}^N(f)]=\sum_{k=K+1}^{\infty}\frac{1}{n^2}\sum_{l=1}^{n}\PE[A^2_{n-l,k}(X^x_{N+l-1})],

@@

where \(\Psi\) is a  class of  functions on \(\mathbb{R}^d.\)

@@

$\Phi_l$ is defined in \eqref{eq:chain_gen} and the expectation is taken according to known distribution \(P_\xi\). Conditioning on $\TrainSet$ underlines that estimation of $\widehat Q_{l}$ derived from training trajectories. In many cases integration can be done in closed analytical form. For example, in the case of ULA algorithm we have \(P_\xi$ is the multivariate normal distribution $ \mathcal{N}(0,I_d)\) and \(\Phi(x,\xi)=x-\gamma\mu(x)+\sqrt{\gamma}\xi.\) Therefore if we use polynomials to approximate \((\bar Q_{l}),\) then \((\widehat a_{l,k})\) can be even computed in closed form; implementations details are provided in  Section~\ref{sec:num}.

@@

\leq \sum_{k=1}^{K}\frac{1}{n^2}\sum_{l=1}^{n}\PE\left[\left.|A_{n-l,k}(X^x_{N+l-1})-\widehat A_{n-l,k}(X^x_{N+l-1})|^2\right | \TrainSet \right].

@@

\begin{lem}
\label{lem:var_poincare}
Under assumptions of Theorem~\ref{th:mr}, it holds
$$
\mathsf{Var}_x\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}\right)\right]\le  \gamma^{-1} C_K (1+V(x)),
$$
where $C_K$ is a constant that does not depend on $q$ and $\gamma.$ 
\end{lem}
\begin{proof}
The expression
$\sum_{p=1}^q \partial_{y_1}^K f(X_p)$
can be viewed as a deterministic function of
$x,Z_1,Z_{2},\ldots,Z_q$
$$
\sum_{p=1}^q  \partial_{y_1}^K f(X_p)
=F(x,Z_1,Z_{2},\ldots,Z_q).
$$
By the (conditional) Gaussian Poincar\'e inequality,
we have
$$
\mathsf{Var}_x\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}\right)\right]
\le\mathsf E_x\left[
\|\nabla_Z F(x,Z_1,Z_{2},\ldots,Z_q)\|^2
\right],
$$
where $\nabla_Z F=(\partial_{Z_1} F,\ldots,\partial_{Z_q} F)$,
and $\|\cdot\|$ denotes the Euclidean norm.
Notice that \(\partial_{Z_j} F=\sqrt{\gamma}\,\partial_{y_j} F\) and
hence
$$
\mathsf{Var}_x\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}\right)\right]\leq\gamma^2\sum_{j=1}^{q}\mathsf{E}_x\left[\left(\sum_{p=1}^{q}\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}\right)\right)^{2}\right].
$$
It is straightforward to check that
$\partial_{y_j}\partial_{y_1}^K f(X_p)=0$
whenever $p<j$. Therefore, we get
\begin{equation}\label{eq:10062018a2}
\mathsf{Var}_x\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}\right)\right]\leq\gamma^2\sum_{j=1}^{q}\mathsf{E}_x\left[\left(\sum_{p=j}^{q}\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}\right)\right)^{2}\right].
\end{equation}
Now fix $p$ and $j$, $p\ge j$, in $\{1,\ldots,q\}$.
By Fa\`a di Bruno's formula
\[
\partial_{y_{1}}^{K}f\left(X_{p}\right)=\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X_{p})\prod_{k=1}^{K}\left(\frac{\partial_{y_{1}}^{k}X_{p}}{k!}\right)^{m_{k}},
\]
where the sum is taken over all $K$-tuples of nonnegative integers
$(m_1,\ldots,m_K)$ satisfying
$$
1\cdot m_{1}+2\cdot m_{2}+\ldots+K\cdot m_{K}=K.
$$
Then
\begin{eqnarray*}
\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}\right)
&=&\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K}+1)}(X_{p})\left[\partial_{y_{j}}X_{p}\right]\prod_{k=1}^{K}\left(\frac{\partial_{y_{1}}^{k}X_{p}}{k!}\right)^{m_{k}} \\
&&+\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X_{p})
\sum_{s=1}^{K}\frac{m_{s}}{s!}
\left(\frac{\partial_{y_{1}}^{s}X_{p}}{s!}\right)^{m_{s}-1}
\\
&& \times\left[\partial_{y_{j}}\partial_{y_{1}}^{s}X_{p}\right]
\prod_{k\le K,\,k\neq s}\left(\frac{\partial_{y_{1}}^{k}X_{p}}{k!}\right)^{m_{k}}.
\end{eqnarray*}
Using the bounds of
Lemmas \ref{lem:06062018a2} and~\ref{lem:06062018a3},
we obtain
\begin{eqnarray}
\label{eq:part-part}
\left|\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}\right)\right|
\leq A_{K}\prod_{k=2}^{p}\alpha_{k}
\end{eqnarray}
with a suitable constant $A_{K}$.
Substituting this in~\eqref{eq:10062018a2},
we proceed as follows
\begin{align*}
\mathsf{Var}_x\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}\right)\right]
&\le
\gamma^2 A_{K}^{2}\sum_{j=1}^{q}
\mathsf{E}\left(\sum_{p=j}^{q}\prod_{k=2}^{p}\alpha_{k}\right)^{2}
\\
&\le
\frac{\gamma^2 A_{K}^{2}}{(1-\gamma B_\mu)^2}
\mathsf{E}\sum_{j=1}^{q}
\left(\sum_{p=j+1}^{q+1}  \prod_{k=2}^{p} \alpha_{k}
\right)^{2}
\\
%&=
%\frac{A_{K}^{2}}{(1-\gamma_1 b_\mu)^2}
%\sum_{j=l}^{q} \gamma_{j}
%\prod_{k=l+1}^{j} \alpha_{k}^2
%\left(
%\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=j+1}^{p} \alpha_{k}
%\right)^{2}
%\\
&\le
\frac{\gamma^2 A_{K}^{2}}{(1-\gamma B_\mu)^3}
\mathsf{E}\sum_{j=1}^{q}
\prod_{k=1}^{j} \alpha_{k}
\left(\sum_{p=j+1}^{q+1}  \prod_{k=j+1}^{p} \alpha_{k}
\right)^{2}
\end{align*}

Now, from the H\"older inequality, we obtain (with $\|X\|_p = (\mathsf{E}X^p)^{\frac{1}{p}}$)
\begin{align*}
\mathsf{E}_x\left[\sum_{j=1}^{q}\prod_{k=l}^{j}\alpha_{k}\left( \sum_{p=j+1}^{q+1}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right] & \leq\sum_{j=1}^{q}\left\Vert \prod_{k=1}^{j}\alpha_{k}\right\Vert _{2}\left\Vert \sum_{p=j+1}^{q+1} \prod_{k=j+1}^{p}\alpha_{k}\right\Vert _{4}^{2}\\
 & \leq\sum_{j=1}^{q} \left\Vert \prod_{k=1}^{j}\alpha_{k}\right\Vert _{2}\left(\sum_{p=j+1}^{q+1}\left\Vert \prod_{k=j+1}^{p}\alpha_{k}\right\Vert _{4}\right)^{2}.
\end{align*}
Now using the fact that $\prod\limits_{k=j+1}^{p}\alpha_{k} \leq \exp\left(-\sum\limits_{k=j+1}^{p}\gamma\mu'(X_{k-1})\right),$
we get
\[
\mathsf{E}_x\left[\sum_{j=1}^{q}\prod_{k=1}^{j}\alpha_{k}\left(\sum_{p=j+1}^{q+1}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right]\leq\sum_{j=1}^{q} \zeta^{1/2}_{1,j}(2) \left(\sum_{p=j+1}^{q+1} \zeta^{1/4}_{j+1,p}(4)\right)^{2},
\]
where we denote
\[
\zeta_{l,j}(u)=\mathsf{E}_x\left[e^{-u\gamma\sum_{k=l}^{j}\mu'(X_{k-1})}\right],\quad u>0.
\]
Note that $\mu^{\prime}(x)$ is bounded due  our assumptions and from Theorem~1 in \cite{delyon1999small} and Lemma~\ref{lem:v_ergodicity} in Appendix~\ref{sec:appendix} it follows that
\[
\mathsf{E}_x\left[e^{-u\gamma\left(\sum_{k=l}^{j}[\mu'(X_{k-1})-\pi_\gamma(\mu')]\right)}\right]\leq C(1+V(x)),\quad u\gamma\leq \gamma_0
\]
for some constants $\gamma_0$ and $C>0$  depending only on $\gamma_0$, provided that $n\gamma^2$ stays bounded. Then we have
\[
\zeta_{l,j}(u)=\mathsf{E}\left[e^{-s\gamma\sum_{k=l}^{j}\mu'(X_{k-1})}\right]\leq  C(1+V(x))e^{-s\gamma (j-l+1)\pi_\gamma(\mu')}.
\]
Furthermore, since $\mu\pi',\mu'\pi\in L^{1}(\mathbb{R})$ and $\pi^{\prime}(x) = -\frac{1}{2}\pi(x)\mu(x)$, we have
\[
\pi(\mu')=\int\mu'(x)\pi(x)\,dx=-\int\mu(x)\pi'(x)\,dx=\frac{1}{2}\int\mu^{2}(x)\pi(x)\,dx>0
\]
Note also that \(\pi_\gamma(\mu^{\prime}) \geq \pi_\gamma(\mu^{\prime}) - C_1\sqrt{\gamma}\)
yielding the bound
\[
\zeta_{l,j}(s) \leq  C(1+V(x))e^{-s\gamma(j-l+1)\alpha}
\]
where $ \alpha = \frac{1}{2}\int \mu^2(x)\pi(x)\,dx - C_1\sqrt{\gamma} > 0$ for sufficiently small $\gamma$. Hence we obtain
\begin{align*}
\sum_{p=j+1}^{q+1} \zeta^{1/4}_{j+1,p}(4) \leq (C(1+V(x)))^{1/4}\sum_{p=j+1}^{q+1}e^{-\gamma(p-j)\alpha} \leq  (C(1+V(x)))^{1/4}\frac{1}{1-e^{- \gamma\alpha}}
\end{align*}
and
\begin{align*}
\sum_{j=1}^{q} \zeta^{1/2}_{1,j}(2) \leq (C(1+V(x)))^{1/2}\sum_{j=0}^{q}e^{-\gamma j\alpha} \leq  (C(1+V(x)))^{1/2}\frac{ 1}{1-e^{- \gamma\alpha}}.
\end{align*}
Thus the final bound follows:
\begin{align*}
\mathsf{Var}_x\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}\right)\right] \leq \gamma^{-1} C_K (1+V(x))
\end{align*}
for $\gamma$ small enough with $C_K$ not depending on $q$. The proof is completed.
\end{proof}

>>>>

\begin{aug}
\author{\snm{D. Belomestny}\thanksref{a,b}\ead[label=e1]{denis.belomestny@uni-due.de}}
\and
\author{\snm{E. Moulines}\thanksref{c, b}\ead[label=e2]{eric.moulines@polytechnique.edu}}
\and
\author{\snm{S. Samsonov}\thanksref{b}\ead[label=e3]{svsamsonov@hse.ru}}
%\and
%\author{\snm{N. Shagadatov}\thanksref{b}\ead[label=e4]{nshagadatov@edu.hse.ru}}

@@

\PVar_x[\pi_{K,n}^N(f)]=\frac{1}{n^2}\sum_{k=K+1}^{\infty}\sum_{l=1}^{n}\PE[A^2_{n-l,k}(X^x_{N+l-1})],

@@

where \(\Psi\) is a  class of  real-valued functions on \(\mathbb{R}^d.\)

@@

$\Phi$ is defined in \eqref{eq:chain_gen} and the expectation is taken according to known distribution \(P_\xi\). Conditioning on $\TrainSet$ underlines that estimation of $\widehat Q_{l}$ derived from training trajectories. In many cases integration can be done in closed analytical form. For example, in the case of ULA algorithm we have \(P_\xi$ is the multivariate normal distribution $ \mathcal{N}(0,I_d)\) and \(\Phi(x,\xi)=x-\gamma\mu(x)+\sqrt{\gamma}\xi.\) Therefore if we use polynomials to approximate \((\bar Q_{l}),\) then \((\widehat a_{l,k})\) can be even computed in closed form; implementations details are provided in  Section~\ref{sec:num}.

@@

\leq \frac{1}{n^2}\sum_{k=1}^{K}\sum_{l=1}^{n}\PE\left[\left.|A_{n-l,k}(X^x_{N+l-1})-\widehat A_{n-l,k}(X^x_{N+l-1})|^2\right | \TrainSet \right].

@@

\begin{lem}
\label{lem:var_poincare}
Under assumptions of Theorem~\ref{th:mr}, it holds
$$
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]\le  \gamma^{-1} C_K (1+V(x)),
$$
where $C_K$ is a constant that does not depend on $q$ and $\gamma.$ 
\end{lem}
\begin{proof}
The expression
$\sum_{p=1}^q \partial_{y_1}^K f(X_p^x)$
can be viewed as a deterministic function of
$x,Z_1,Z_{2},\ldots,Z_q$
$$
\sum_{p=1}^q  \partial_{y_1}^K f(X_p^x)
=F(x,Z_1,Z_{2},\ldots,Z_q).
$$
By the (conditional) Gaussian Poincar\'e inequality,
we have
$$
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]
\le\mathsf E_x\left[
\|\nabla_Z F(x,Z_1,Z_{2},\ldots,Z_q)\|^2
\right],
$$
where $\nabla_Z F=(\partial_{Z_1} F,\ldots,\partial_{Z_q} F)$,
and $\|\cdot\|$ denotes the Euclidean norm.
Notice that \(\partial_{Z_j} F=\sqrt{\gamma}\,\partial_{y_j} F\) and
hence
$$
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]\leq\gamma^2\sum_{j=1}^{q}\mathsf{E}\left[\left(\sum_{p=1}^{q}\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right)^{2}\right].
$$
It is straightforward to check that
$\partial_{y_j}\partial_{y_1}^K f(X_p^x)=0$
whenever $p<j$. Therefore, we get
\begin{equation}\label{eq:10062018a2}
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]\leq\gamma^2\sum_{j=1}^{q}\mathsf{E}\left[\left(\sum_{p=j}^{q}\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right)^{2}\right].
\end{equation}
Now fix $p$ and $j$, $p\ge j$, in $\{1,\ldots,q\}$.
By Fa\`a di Bruno's formula
\[
\partial_{y_{1}}^{K}f\left(X_{p}^x\right)=\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X_{p}^x)\prod_{k=1}^{K}\left(\frac{\partial_{y_{1}}^{k}X^x_{p}}{k!}\right)^{m_{k}},
\]
where the sum is taken over all $K$-tuples of nonnegative integers
$(m_1,\ldots,m_K)$ satisfying
$$
1\cdot m_{1}+2\cdot m_{2}+\ldots+K\cdot m_{K}=K.
$$
Then
\begin{eqnarray*}
\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)
&=&\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K}+1)}(X^x_{p})\left[\partial_{y_{j}}X^x_{p}\right]\prod_{k=1}^{K}\left(\frac{\partial_{y_{1}}^{k}X_{p}^x}{k!}\right)^{m_{k}} \\
&&+\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X^x_{p})
\sum_{s=1}^{K}\frac{m_{s}}{s!}
\left(\frac{\partial_{y_{1}}^{s}X^x_{p}}{s!}\right)^{m_{s}-1}
\\
&& \times\left[\partial_{y_{j}}\partial_{y_{1}}^{s}X^x_{p}\right]
\prod_{k\le K,\,k\neq s}\left(\frac{\partial_{y_{1}}^{k}X^x_{p}}{k!}\right)^{m_{k}}.
\end{eqnarray*}
Using the bounds of
Lemmas \ref{lem:06062018a2} and~\ref{lem:06062018a3},
we obtain
\begin{eqnarray}
\label{eq:part-part}
\left|\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right|
\leq A_{K}\prod_{k=2}^{p}\alpha_{k}
\end{eqnarray}
with a suitable constant $A_{K}$.
Substituting this in~\eqref{eq:10062018a2},
we proceed as follows
\begin{align*}
\mathsf{Var}_x\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]
&\le
\gamma^2 A_{K}^{2}\sum_{j=1}^{q}
\mathsf{E}\left(\sum_{p=j}^{q}\prod_{k=2}^{p}\alpha_{k}\right)^{2}
\\
&\le
\frac{\gamma^2 A_{K}^{2}}{(1-\gamma B_\mu)^2}
\mathsf{E}\sum_{j=1}^{q}
\left(\sum_{p=j+1}^{q+1}  \prod_{k=2}^{p} \alpha_{k}
\right)^{2}
\\
%&=
%\frac{A_{K}^{2}}{(1-\gamma_1 b_\mu)^2}
%\sum_{j=l}^{q} \gamma_{j}
%\prod_{k=l+1}^{j} \alpha_{k}^2
%\left(
%\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=j+1}^{p} \alpha_{k}
%\right)^{2}
%\\
&\le
\frac{\gamma^2 A_{K}^{2}}{(1-\gamma B_\mu)^3}
\mathsf{E}\sum_{j=1}^{q}
\prod_{k=1}^{j} \alpha_{k}
\left(\sum_{p=j+1}^{q+1}  \prod_{k=j+1}^{p} \alpha_{k}
\right)^{2}
\end{align*}

Now, from the H\"older inequality, we obtain (with $\|X\|_p = (\mathsf{E}X^p)^{\frac{1}{p}}$)
\begin{align*}
\mathsf{E}\left[\sum_{j=1}^{q}\prod_{k=l}^{j}\alpha_{k}\left( \sum_{p=j+1}^{q+1}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right] & \leq\sum_{j=1}^{q}\left\Vert \prod_{k=1}^{j}\alpha_{k}\right\Vert _{2}\left\Vert \sum_{p=j+1}^{q+1} \prod_{k=j+1}^{p}\alpha_{k}\right\Vert _{4}^{2}\\
 & \leq\sum_{j=1}^{q} \left\Vert \prod_{k=1}^{j}\alpha_{k}\right\Vert _{2}\left(\sum_{p=j+1}^{q+1}\left\Vert \prod_{k=j+1}^{p}\alpha_{k}\right\Vert _{4}\right)^{2}.
\end{align*}
Now using the fact that $\prod\limits_{k=j+1}^{p}\alpha_{k} \leq \exp\left(-\sum\limits_{k=j+1}^{p}\gamma\mu'(X_{k-1}^x)\right),$
we get
\[
\mathsf{E}\left[\sum_{j=1}^{q}\prod_{k=1}^{j}\alpha_{k}\left(\sum_{p=j+1}^{q+1}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right]\leq\sum_{j=1}^{q} \zeta^{1/2}_{1,j}(2) \left(\sum_{p=j+1}^{q+1} \zeta^{1/4}_{j+1,p}(4)\right)^{2},
\]
where we denote
\[
\zeta_{l,j}(u)=\mathsf{E}\left[e^{-u\gamma\sum_{k=l}^{j}\mu'(X^x_{k-1})}\right],\quad u>0.
\]
Note that $\mu^{\prime}(x)$ is bounded due  our assumptions and from Theorem~1 in \cite{delyon1999small} and Lemma~\ref{lem:v_ergodicity} in Appendix~\ref{sec:appendix} it follows that
\[
\mathsf{E}\left[e^{-u\gamma\left(\sum_{k=l}^{j}[\mu'(X^x_{k-1})-\pi_\gamma(\mu')]\right)}\right]\leq C(1+V(x)),\quad u\gamma\leq \gamma_0
\]
for some constants $\gamma_0$ and $C>0$  depending only on $\gamma_0$, provided that $n\gamma^2$ stays bounded. Then we have
\[
\zeta_{l,j}(u)=\mathsf{E}\left[e^{-s\gamma\sum_{k=l}^{j}\mu'(X^x_{k-1})}\right]\leq  C(1+V(x))e^{-s\gamma (j-l+1)\pi_\gamma(\mu')}.
\]
Furthermore, since $\mu\pi',\mu'\pi\in L^{1}(\mathbb{R})$ and $\pi^{\prime}(x) = -\frac{1}{2}\pi(x)\mu(x)$, we have
\[
\pi(\mu')=\int\mu'(x)\pi(x)\,dx=-\int\mu(x)\pi'(x)\,dx=\frac{1}{2}\int\mu^{2}(x)\pi(x)\,dx>0
\]
Note also that \(\pi_\gamma(\mu^{\prime}) \geq \pi_\gamma(\mu^{\prime}) - C_1\sqrt{\gamma}\)
yielding the bound
\[
\zeta_{l,j}(s) \leq  C(1+V(x))e^{-s\gamma(j-l+1)\alpha}
\]
where $ \alpha = \frac{1}{2}\int \mu^2(x)\pi(x)\,dx - C_1\sqrt{\gamma} > 0$ for sufficiently small $\gamma$. Hence we obtain
\begin{align*}
\sum_{p=j+1}^{q+1} \zeta^{1/4}_{j+1,p}(4) \leq (C(1+V(x)))^{1/4}\sum_{p=j+1}^{q+1}e^{-\gamma(p-j)\alpha} \leq  (C(1+V(x)))^{1/4}\frac{1}{1-e^{- \gamma\alpha}}
\end{align*}
and
\begin{align*}
\sum_{j=1}^{q} \zeta^{1/2}_{1,j}(2) \leq (C(1+V(x)))^{1/2}\sum_{j=0}^{q}e^{-\gamma j\alpha} \leq  (C(1+V(x)))^{1/2}\frac{ 1}{1-e^{- \gamma\alpha}}.
\end{align*}
Thus the final bound follows:
\begin{align*}
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X^x_{p}\right)\right] \leq \gamma^{-1} C_K (1+V(x))
\end{align*}
for $\gamma$ small enough with $C_K$ not depending on $q$. The proof is completed.
\end{proof}
